\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-08-11 doc/paper.tex
Abstract revisions

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} Spreadsheet environments often come equipped with an abundance
		of functions and operations to manipulate data, which users can combine into
		complex formulae. However, anticipating these combinations is difficult,
		complicating matters for both researchers and practitioners who want to study
		formulae to improve spreadsheet practices. Therefore, we developed
		\toolnameend, a tool that analyzes spreadsheet corpora to visualize patterns of
		function combination as an interactive tree, capable of representing both the
		most common and most anomalous patterns of formula construction and their
		contexts in actual workbooks. Using spreadsheets from the Enron corpus, we
		conduct both a case study and a user study to explore \toolnameposs various
		applications, particularly those in flexible smell detection and spreadsheet
		education.

>>>>

	% As a general rule, do not put math, special symbols or citations
	% in the abstract
	\begin{abstract} Spreadsheet environments offer many
		functions to manipulate data, which users can combine into
		complex formulae. However, for both researchers and practitioners who want to
		study formulae to improve spreadsheet practices, anticipating these
		combinations is difficult. Therefore, we developed \toolnameend, a tool that
		analyzes spreadsheet collections to visualize patterns of function combination
		as an interactive tree, representing both the most common and most anomalous
		patterns of formula construction and their contexts. Using spreadsheets from
		the Enron corpus, we conduct a case study and a user study to explore
		\toolnameposs various applications, such as those in flexible smell
		detection and spreadsheet education.
